Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-04 paper.tex
fixing references

\begin{itemize}
\item \textbf{Bagging} 
Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced by \citet{B1996}. Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset. The new generated datasets are drawn randomly with replacement in a size almost equal to the original dataset. The final classifier's output is based on aggregating the classifiers by taking a majority or weighted vote.

\item \textbf{Boosting} 
Boosting is an ensemble classification algorithm which was first proposed by \citet{schapire1990strength} in \citet{schapire1990strength}. Boosting is based on the idea that a set of weak classifiers can create a stronger one. In this work we adopt a powerful a variation of boosting called Adaptive Boosting or ''Adaboost'' for short \cite{FS1997}. Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.

@@

\item \textbf{Random Forest}
This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman in \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
The result is the average of the generated trees during the process.
\end{itemize}

>>>>

\begin{itemize}
\item \textbf{Bagging}: 
Bagging which is called also Bootstrap aggregating is an ensemble meta-algorithm introduced in \cite{B1996}. Bagging works by training base classifiers (usually decision tree classifiers) based on generated new datasets from the original training dataset. The new generated datasets are drawn randomly with replacement in a size almost equal to the original dataset. The final classifier's output is based on aggregating the classifiers by taking a majority or weighted vote.

\item \textbf{Boosting}: 
Boosting is an ensemble classification algorithm which was first proposed in \cite{schapire1990strength}. Boosting is based on the idea that a set of weak classifiers can create a stronger one. In this work we adopt a powerful a variation of boosting called Adaptive Boosting or ''Adaboost'' for short \cite{FS1997}. Adaboost operates on a training dataset ${(x_{1},y_{1}),...,(x_{m},y_{m})}$ where each $x_{i}$ is a set of inputs belongs to some domain $X$ and each $y_{i}$ belongs to some label $Y$ assuming $Y$ is a binary class set $\{+1,-1\}$.

@@

\item \textbf{Random Forest}:
This method is based on the construction of a set of decision trees using a stochastic process over the basis of C4.5 algorithm. It was proposed by Breiman in \cite{Breiman2001} and aims to create independent and uncorrelated trees based on different and random input vectors, following the same distribution. 
The result is the average of the generated trees during the process.
\end{itemize}
